Experimenting with n-grams in Civil Procedure Codes

### 2014-08-05 experiment.Rmd
Filter unreasonable n-grams

That kind of analysis might be generally useful, so let's turn it into a function.

@@

  matches <- intersect(orig_code, dest_code)
  shared_ngrams <- unique(c(orig_code, dest_code))
  ratio_matches_to_possible <- length(matches) / length(shared_ngrams)
  ratio_matches_to_destination <- length(matches) / length(dest_code)
  list(matches = matches,
       shared_ngrams = shared_ngrams,
       ratio_matches_to_possible = ratio_matches_to_possible,
       ratio_matches_to_destination = ratio_matches_to_destination)
}
```

>>>>

That kind of analysis might be generally useful, so let's turn it into a function. First a helper function that removes elements from the list of n-grams. A lot of the n-grams contain non-word characters, numbers, or gibberish from the OCR. We want to know the proportion of matches that could be reasonably matched, so we'll exclude n-grams containing any of those characters.

```{r}
#' Remove unreasonable n-grams containing characters other than letters and spaces
#' @param ngrams A list of n-grams
#' @return Returns a list of filtered n-grams
filter_unreasonable_ngrams <- function(ngrams) {
  require(stringr)
  ngrams[!str_detect(ngrams, "[^a-z ]")]
}
```

Now the main function for comparing two codes:

@@

  matches <- intersect(orig_code, dest_code)
  shared_ngrams <- unique(c(orig_code, dest_code))
  ratio_matches_to_possible <- length(matches) / length(filter_unreasonable_ngrams(shared_ngrams))
  ratio_matches_to_destination <- length(matches) / length(filter_unreasonable_ngrams(dest_code))
  list(matches = matches,
       shared_ngrams = shared_ngrams,
       ratio_matches_to_possible = ratio_matches_to_possible,
       ratio_matches_to_destination = ratio_matches_to_destination)
}
```
